asc_file_database

### 2019-03-12 src/stack_test.Rmd
minor change

>>>>

testing model fiddling

```{r}
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0
prab <- rbind(janpres, janab)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables
prab

test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)

system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")
mod1 <- maxent(x = prab, p = pa)

pre1 <- predict(mod1, test, args='outputformat=raw' ) #, args = c("outputformat=cloglog")
preplot <- plot(pre1)
preplot
